---
title: "The Inequality and Quality of Education"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(dplyr)
library(plotly)
library(ggplot2)
computeStu = function(...) return(3435)
computeSecS = function(...) return(19)
computePriS = function(...) return(148)
```



```{r data}
data<-read.csv("D:/MED/DAT VIS/example_data.csv")
data$SID<-as.character(data$SID)
data$PID<-as.character(data$PID)
names(data)[2] <- "Achievement_M3"
names(data)[3] <- "Achievement_P6"
names(data)[5] <- "Gender"
names(data)[7] <- "SecondarySchool_ID"
names(data)[8] <- "PrimarySchool_ID"
Categorical.Variables = c("Gender", "SecondarySchool_ID", "PrimarySchool_ID")

Numerical.Variables = c("Achievement_M3", "Achievement_P6", "SOC")
```

Sidebar {.sidebar data-width=200}
=======================================================================

```{r}
selectInput("categorical_variable", label = "Select Categorical Variable:", choices = Categorical.Variables)

selectInput("numerical_variable", label = "Select Numerical Variable:", choices = Numerical.Variables)

```


Information {data-icon="fa-info-circle"}
=======================================================================

Row 
-----------------------------------------------------------------------

### Total Students

```{r}
students = computeStu()
valueBox(students, icon = "fa-users", color = "red")
```

### Total Secondary Schools

```{r}
secschool = computeSecS()
valueBox(secschool, icon = "fa-university", color = "orange")
```


### Total Primary Schools

```{r}
prischool = computePriS()
valueBox(prischool, icon = "fa-university", color = "green")
```


Row
--------------------------
### **Box plot** shows the relationship between categorical and numerical variables {data-width=700}

```{r}
renderPlotly({
  plot_ly(data,
              x = ~data[[input$numerical_variable]],
              color = ~data[[input$categorical_variable]],
              colors = "Paired",
              type = "box") %>%
  layout(title = "",
         xaxis = list(title = "" ,
                      zeroline = FALSE))
})

```


### **Bar chart** shows the distribution of categorical variable {data-width=500}

```{r}
renderPlotly({
  data %>%
    count(var = data[[input$categorical_variable]], name = "count") %>%
    plot_ly( x = ~var, y = ~ count, type = "bar", marker = list(color = '#008ae6',line = list(color = '#008ae6', width = 2)), hoverinfo = "x+y") %>%
    add_text(text = ~paste0( " (",   scales::percent(count/sum(count)),")"), 
           textposition = "bottom", 
           textfont = list(size = 8, color = "white"), 
           showlegend = FALSE) %>%
    layout(xaxis = list(title = ""), yaxis = list(title = ""))
    
})
```


### **Histogram** shows the distribution of numerical variable {data-width=500} 

```{r}
renderPlotly({
  plot_ly(x = data[[input$numerical_variable]], type = "histogram",  marker = list(color = "#008ae6", line = list(color = "darkgray", width = 1)))
})
```


Quality {data-icon="fa-bar-chart"} 
=======================================================================

Row 
-----------------------------------------------------------------------

### Average ACH_M3_Male

```{r}
M3M<-data%>%group_by(Gender)%>%filter(Gender=="Male")%>%summarise(Achievement_M3=mean(Achievement_M3))
gauge(5.42, min = 0, max = 10,gaugeSectors(
  success = c(8,10), warning = c(40,79), danger = c(0,39)
))
```

### Average ACH_M3_Female

```{r}
M3F<-data%>%group_by(Gender)%>%filter(Gender=="Female")%>%summarise(Achievement_M3=mean(Achievement_M3))
gauge(5.94, min = 0, max = 10,gaugeSectors(
  success = c(8,10), warning = c(40,79), danger = c(0,39)
))
```

### Average ACH_P6_Male

```{r}
P6M<-data%>%group_by(Gender)%>%filter(Gender=="Male")%>%summarise(Achievement_P6=mean(Achievement_P6))
gauge(96.5, min = 0, max = 150,gaugeSectors(
  success = c(41,50), warning = c(21,40), danger = c(0,20)
))
```

### Average ACH_P6_Female

```{r}
P6M<-data%>%group_by(Gender)%>%filter(Gender=="Female")%>%summarise(Achievement_P6=mean(Achievement_P6))
gauge(99.1, min = 0, max = 150,gaugeSectors(
  success = c(41,50), warning = c(21,40), danger = c(0,20)
))
```


Row 
-----------------------------------------------------------------------

### Show the Achievement of M3 {data-width=500}
```{r}
renderPlotly({
  plot_ly(data, 
        x = ~Achievement_M3, 
        color = ~data[[input$categorical_variable]], 
        type = 'histogram')%>% layout(title = "",  
                      xaxis = list(title = "") )
})
```


### Show the Achievement of P6 {data-width=500}
```{r}
renderPlotly({
  plot_ly(data, 
        x = ~Achievement_P6, 
        color = ~data[[input$categorical_variable]], 
        type = 'histogram')%>% layout(title = "",  
                      xaxis = list(title = "") )
})
```


Inequality {data-icon="fa-bar-chart"}
=======================================================================

Row 
-----------------------------------------------------------------------

### Percentage of students with low SOC

```{r}
lowSOC<-data%>%filter(SOC=="0"|SOC=="1")
valueBox(70.80, icon = "fa-percent", color = "blue")
```

### Percentage of students with median SOC

```{r}
midSOC<-data%>%filter(SOC=="20")
valueBox(20.55, icon = "fa-percent", color = "darkorchid")
```


### Percentage of students with high SOC

```{r}
highSOC<-data%>%filter(SOC=="31")
valueBox(8.65, icon = "fa-percent", color = "magenta")
```


column
-----------------------------------------------------------------------


### Show the Inequality of M3 with low SOC {data-width=500}
```{r}
ACH_M3_SOC01<-data%>%group_by(SecondarySchool_ID)%>%filter(SOC=="0"|SOC=="1")%>%summarise(ACH_M3_SOCL=mean(Achievement_M3))
ACH_M3_SOC20<-data%>%group_by(SecondarySchool_ID)%>%filter(SOC=="20")%>%summarise(ACH_M3_SOCM=mean(Achievement_M3))
ACH_M3_SOC31<-data%>%group_by(SecondarySchool_ID)%>%filter(SOC=="31")%>%summarise(ACH_M3_SOCH=mean(Achievement_M3))
#ACH_M3_SOC01
ggplot(ACH_M3_SOC01, aes(x=SecondarySchool_ID, y=ACH_M3_SOCL, color=SecondarySchool_ID)) + 
  geom_point(size=6) + 
  geom_line() +   
  geom_hline(yintercept = 5.678603)+
  labs(x = "School No. of Low SOC") +
  labs(y = "Achievement") +
  theme(legend.position = "none")
```

### Show the Inequality of M3 with median SOC {data-width=500}
```{r}
#ACH_M3_SOC20
ggplot(ACH_M3_SOC20, aes(x=SecondarySchool_ID, y=ACH_M3_SOCM, color=SecondarySchool_ID)) + 
  geom_point(size=6) + 
  geom_line() +   
  geom_hline(yintercept = 5.678603)+
  labs(x = "School No. of Median SOC") +
  labs(y = "Achievement")+
  theme(legend.position = "none")
```

### Show the Inequality of M3 with high SOC {data-width=500}
```{r}
#ACH_M3_SOC31
ggplot(ACH_M3_SOC31, aes(x=SecondarySchool_ID, y=ACH_M3_SOCH, color=SecondarySchool_ID)) + 
  geom_point(size=6) + 
  geom_line() +   
  geom_hline(yintercept = 5.678603)+
  labs(x = "School No of Hight SOC") +
  labs(y = "Achievement") +
  theme(legend.position = "none")
```

column {data-width=500}
------------------------------
### Show the Inequality of P6 with low SOC {data-width=500}
```{r}
ACH_P6_SOC01<-data%>%group_by(PrimarySchool_ID)%>%
  filter(SOC=="0"|SOC=="1")%>%summarise(ACH_P6_SOCL=mean(Achievement_P6))
ACH_P6_SOC20<-data%>%group_by(PrimarySchool_ID)%>%
  filter(SOC=="20")%>%summarise(ACH_P6_SOCM=mean(Achievement_P6))
ACH_P6_SOC31<-data%>%group_by(PrimarySchool_ID)%>%
  filter(SOC=="31")%>%summarise(ACH_P6_SOCH=mean(Achievement_P6))

#ACH_P6_SOC01
ggplot(ACH_P6_SOC01, aes(x=PrimarySchool_ID, y=ACH_P6_SOCL, color=PrimarySchool_ID)) + 
  geom_point(size=6) + 
  geom_line() +   
  geom_hline(yintercept = 97.8)+
  labs(x = "School No. of Low SOC") +
  labs(y = "Achievement")+
  theme(legend.position = "none")
```

### Show the Inequality of P6 with median SOC {data-width=500}
```{r}
#ACH_P6_SOC20
ggplot(ACH_P6_SOC20, aes(x=PrimarySchool_ID, y=ACH_P6_SOCM, color=PrimarySchool_ID)) + 
  geom_point(size=6) + 
  geom_line() +   
  geom_hline(yintercept = 97.8)+
  labs(x = "School No. of Median SOC") +
  labs(y = "Achievement")+
  theme(legend.position = "none")
```

### Show the Inequality of P6 with high SOC {data-width=500}
```{r}
#ACH_P6_SOC31
ggplot(ACH_P6_SOC31, aes(x=PrimarySchool_ID, y=ACH_P6_SOCH, color=PrimarySchool_ID)) + 
  geom_point(size=6) + 
  geom_line() +   
  geom_hline(yintercept = 97.8)+
  labs(x = "School No of Hight SOC") +
  labs(y = "Achievement") +
  theme(legend.position = "none")
```
